\newpage
\thispagestyle{plain}
\pagenumbering{roman}
    
    \Large
    \textbf{Acknowledgments}

	\vspace{1cm}

	\normalsize

    This dissertation wouldn't have been possible without the help and support of many others.  I'd like to thank my advisor, Carter Hall, for allowing me to work with him over the past five years.  I appreciate all of the advice you have given me, and everything you have taught me over the years.  The quality of my research, writing, and communication has improved drastically, due in large part to your guidance.

In a similar vein, I'd like to thank my coworkers in the Experimental Nuclear Physics Group.  Thank you to Tom, Simon, Ruey, Clayton, Attila, and Jon for the excellent research group which you helped build.  I owe particular thanks to Attila,  who helped me develop my analysis skills, and always encouraged me to get involved in on-going LUX work. 
    
I would also like to thank all of my LUX coworkers.  Our long days in South Dakota, and our countless meetings have paid off.  I appreciate all of your hard work, without which this dissertation would not exist.  To Lucie, Mark, Mongkol, Dev, Elizabeth, Curt, Carmen, Markus, Paul, Alex M., Alex L., and the many others who I spent time on site with, thank you for making the long stays more bearable with board games, cook outs, and experiences in the Black Hills.  To Scott, Matthew, and Kevin O., thank you for the many informative conversations we've had about light yields, electric fields, and physics in general.  Many of your ideas have found their way into this work.

Thank you to my peers at Maryland, who helped me make it through classes and qualifiers.  I owe a lot to Zach, Andrew, Young, and Chris, for answering my countless questions during the classes we took, and for helping me keep up with the amazing students from our year.  To Ryan, Jack, Nat, George, Kevin, Joe, Jake, Aimee, and the four mentioned above, thanks for all the fun times outside of school.  The concerts, cook outs, movie nights, board games, and made up holidays made the stressful times in graduate school much more manageable.  

Thank you to my family, for always supporting me and doing everything they can to help me succeed.  Mom and Dad, I appreciate all of your hard work and dedication, which have given me the privilege to go to college and graduate school.  Thank you for teaching me to always improve myself, and for instilling a strong work ethic in me.  Andrew, thank you for the years of brotherly love and competition, which have always pushed me to do my best.  Matthew, thank you for constantly reminding me to improve as a person, as well as a graduate student.  Your kindness, humor, and honesty have helped keep the overwhelming world of graduate school in perspective over the past five years.
 
Last, but certainly not least, I'd like to thank Myra.  Thank you for being by my side through the vast majority of my time in graduate school.  As you already know, many of the ideas presented here came to me while you patiently, and thoughtfully, listened to details about my work.  Your company over the past four and a half years, and all of the goofy moments we have spent together have made my time in graduate school fly by.
 
There are many others who have helped me over the years who I didn't mention here.  Your support is equally appreciated, and I apologize if it has been inadvertently left out.

    
    
